\section{Kubernetes Internals}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{kubeadm}

{\footnotesize \textit{To build your own k8s cluster, install node machines / OSes, with relevant network config and container runtimes, then run:}}\\
\entry{30mm}{kubeadm init}{run on master node}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Controllers (\& k8s ``Control Plane'')}
{\footnotesize \textit{These are a bevy of subscribers to API server, each listening for events of interest. They affect cluster $\Delta$s by writing back to API server. Egs:}}\\[-2mm]
\api
{2.0cm}{
Replc'n Mgr     \\
StatefulSet C.  \\
Job C.          \\
Namespace C.    

}
{2.0cm}{
ReplicaSet C.   \\
Node C.         \\
Service C.      \\
Persist.Vol. C. 

}
{2.0cm}{
DaemonSet C.    \\
Deployment C.   \\
Endpoints C.    

}
\stopapi



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Scheduler}
{\footnotesize \textit{Assigns pod $\to$ node by $\Delta$-ing pod definition thru API server, which then notifies {\tt kubelet} of the $\Delta$.}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{kubelet}
{\footnotesize \textit{Monitors API server for pods assigned to the local node; then starts new pods' containers by invoking the cluster's configured container runtime (most often Docker).}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{kube-dns}
{\footnotesize \textit{A pod that $\exists$ ($\in$ {\tt kube-system}) to resolve cluster service URLs to service IPs $\forall$ pods $\in$ the cluster. DNS inquiries are routed here by default; each \ul{each} pod's {\tt /etc/resolv.conf} file points to {\tt kube-dns}.}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{kube-proxy}
\textit{Each node has a {\tt kube-proxy} that writes {\tt EndPoints} contents to its node's {\tt iptables} file.}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\href{https://github.com/kubernetes/community/blob/master/contributors/design-proposals/architecture/resource-management.md}{API}}

{\footnotesize \textit{API adheres to \href{https://en.wikipedia.org/wiki/Representational\_state\_transfer}{REST} principals, employing HTTP (or \href{https://developers.google.com/protocol-buffers}{protobufs}) to transfer data. REST's ``\href{https://martinfowler.com/articles/richardsonMaturityModel.html\#level1}{resources}'' map to k8s ``\href{https://kubernetes.io/docs/concepts/overview/working-with-objects/kubernetes-objects/\#kubernetes-objects}{objects}'' (eg, pods, namespaces, etc) via its ``\href{https://stackoverflow.com/questions/52309496/difference-between-kubernetes-objects-and-resources}{resource}'' URL. {\tt kubectl} CLI wraps HTTP calls. Most/all resources have the following:}}\\
\texttt{[top level]}\quad\textit{(top level fields)}\\[-2mm]
\api
{1.5cm}{
apiVersion  
}
{1.0cm}{
kind        
}
{1.3cm}{
metadata
}
{1.0cm}{
spec
}
{1.0cm}{
status
}
\stopapi
\\
\texttt{[resource].metadata}\quad\textit{(generic, $\forall$ resource)}\\[-2mm]
\api
{2.0cm}{
name        \\
labels      \\
manag'dFields\\
del.Time'p  \\
rs'ceVersion

}
{2.0cm}{
generateName    \\
annotations     \\
ownerRef's      \\
del.Gr'cPer.Sec's\\
selfLink        

}
{2.0cm}{
namespace   \\
finalizers  \\
creat'nTim'p\\
generation  \\
uid

}
\stopapi
\\
\texttt{[<rsrcetype>List]}\quad\textit{(collect'n, <rsrcetype>s)}\\[-2mm]
\api
{1.5cm}{
apiVersion

}
{1.5cm}{
kind

}
{1.5cm}{
metadata

}
{1.5cm}{
items

}
\stopapi

\textit{Eg, for a ChronJob (other fields are obj-specific):}\\
\code{apiVersion: batch/v1; kind: ChronJob} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Client libraries}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Networking}
%\textit{Services expose pods behind two layers of indirection: 1) a Service url, which {\tt kube-dns} resolves to a singular service IP; 2) an EndPoints that maps the service IP to a list of randomly-chosen pod IPs. Ingresses (L7) and LoadBalancers (L4) can then expose services externally by redirecting requests made against a given public IP.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Custom Resource Definitions}

